A holomorphic approach to membranes and fivebranes

### 2022-06-15 fivebranes/twisted.tex
states

@@

>>>>

\parsec[s:twistedsugra]

In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze `twisted $M$ theory'. 
This theory is obtained from \brian{finish}

@@

\parsec[s:brkevin]

As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \C \times C$, where $C$ is a Riemann surface, with some number of twisted `fivebranes' wrapping 
\[
0 \times 0 \times C \subset \R \times \C \times C .
\]
It will be convenient to view $\R \times \C \times C$ as the total space of the real rank two bundle $\R \oplus K_C$ over $C$. 
Removing the zero section and deforming by the backreaction associated to $C$ corresponds to the twisted version of the $S^2 \times AdS_3$ background. 
We proceed to describe the twisted version of states at the boundary of this version of $AdS$. 
We first proceed before turning on the backreaction.

If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection ${\rm Tot}(\R \oplus K_C) \to \R_+ \times C$ which combines the fiberwise norm with the natural bundle projection.
Denote by $r$ a coordinate for the direction $\R_+$ normal to the brane and let $z \in C$ be a local holomorphic coordinate. 
The fibers of this projection away from $r = 0$ are all homeomorphic to the two-sphere.

Compactification along this projection results in a theory with infinitely many Kaluza--Klein modes roughly parametrized by the Cauchy--Riemann cohomology of the two sphere as a hypersurface in $\R \oplus K_C|_z \simeq \R \times \C$. 
We will elaborate on the appearance of this sort of cohomology momentarily.
The theory admits a natural `vacuum' boundary condition at $r=0$.
In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.

The `supergravity states' are, by definition, fields which satisfy the linearized equations of motion and satisfy the vacuum boundary condition except at a single point. 
The linearized equations of motion are simply $(\d_{dR} + \dbar) \alpha = 0$. 
Thus, up to equivalence, all solutions to the linearized equations of motion are constant in the real variable $t$, and holomorphic in $z,w$.

Modifications of the boundary condition at the point $z = 0$ on the boundary take the form
\[
\alpha = f(w) \delta^{(r)}_{z=0} 
\]
where $f$ is some holomorphic function. 
Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$. 
It is convenient to parameterize such boundary modifications algebraically by expressions of the form 
\[
\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
\]

\brian{finish}
